### 2014-08-13 fundamentals/intro.tex
adds a sentence to the intro about why agent based alternative is good.
additions to intro

In nuclear fuel cycle simulation, it is necessary to calculate and optimize 
nuclear process physics, facility deployment, and material routing in order to 
capture overall fuel cycle performance metrics.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to very high-fidelity industrial 
models.

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform.

@@

Simulators drive R\&D by calculating metrics that can be compared accross fuel 
cycles.

Previous simulators have been static or dynamic. Some have been discrete while 
others have been fleet-based. Some have captured regional behavior, material 
isotopics, transmutation detail, etc. Indeed, some tools have attempted 
agent-based functionality.

Historically, the national laboratories have driven development and regulated 
the use of their own tools (cite VISION, DANESS, NFCSim, etc.), while 
universities and industry have simultaneously developed tools of their own as 
well.

The Cyclus code arose out of the GENIUSv2 code. That software itself was the 
result of lessons-learned from an LDRD project at INL called GENIUSv1.

>>>>

In order to capture fuel cycle performance metrics, nuclear fuel cycle analysis 
requires calculation and optimization of myriad physical, nuclear, chemical, industrial, 
and political phenomena. Nuclear process physics, facility 
deployment, and material routing each represent complex systems that must be 
modeled simultaneously for even the simplest of nuclear fuel cycle analyses.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to very high-fidelity 
industrial models.  To date, current tools are either static, fleet-based, or 
privately distributed.  An alternative to these approaches is a dynamic, 
agent-based simulator with an open platform.

Modern insight indicates that dynamic nuclear 
fuel cycle analysis more generically supports a broad range of simulation goals 
\cite{piet_dynamic_2011}. Similarly, experience in the greater field of systems 
analysis indicates that agent-based modeling supports a greater range of 
simulations, without loss of generality \cite{thatpapermattsent}. Finally, 
openness allows access, cross-institutional collaboration, and increases code 
robustness \cite{softwarecarpentryresource}.

Myriad challenges in nuclear fuel cycle analysis could be 
addressed with an agent-based framework for simulation and tracking of 
transformation and trade of resources between facilities within institutions 
and regions.

@@

Simulators drive \gls{RDD} by calculating metrics that can be compared across fuel 
cycles.

Previous simulators have been static or dynamic. Some have been discrete while 
others have been fleet-based. Some capture regional behavior, material 
isotopics, and transmutation detail, while others do not. Indeed, some tools 
have attempted agent-based functionality.

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{<++>}, 
\gls{DANESS}\cite{<++>}, \gls{DYMOND}\cite{<++>}, and \gls{NFCSim}\cite{<++>}, 
while universities and industry have simultaneously developed tools of their 
  own as well, such as \gls{CAFCA}\cite{<++>}.

The Cyclus code arose out of the \gls{GENIUSv2}\cite{<++>} code. That software 
itself was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL} called \gls{GENIUSv1}\cite{<++>}.
